Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is a merged and final version of two conference papers, \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}, with a unified and streamlined presentation.}

### 2020-07-17 journal paper/content/sec-bg.tex
Minor edits.

\item Exploration-separating algorithms can achieve
    $\BIR(t) = \tildeO\rbr{t^{-1/3}}$
for all priors, \eg by using Epsilon-Greedy with exploration probability $\eps_t = t^{-1/3}$ in each round $t$.
The $t^{-1/3}$ rate is the best possible in the worst case, in the following sense:
    $\BIR(t) = \tildeO\rbr{t^{-\gamma}}$
for all $t$ and some $\gamma>0$,
over all problem instances, then $\gamma\geq \nicefrac{1}{3}$. This is by \eqref{eq:bg-BReg} and the fact that $\BReg(T)\geq \Omega(T^{2/3})$ in the worst case. (The latter follows from the `frequentist" lower bound in \citet{MechMAB-ec09}.)

\item Adaptive-exploration algorithms \emph{can} have an even better regret rate: $\BIR(t) = \tildeO\rbr{ t^{-1/2} } $. This holds for Successive Elimination \citep{EvenDar-icml06} and for Thompson Sampling (see Appendix~\ref{app:MAB-monotone-smart}).% 
    \footnote{However, such result is not known for UCB1 algorithm, to the best of our knowledge.}
    Any optimal MAB algorithm enjoys this regret rate ``on average" by \eqref{eq:bg-BReg}, since 
        $\BReg(T)\leq \tildeO(\sqrt{T})$.
    In particular, if such algorithm satisfies
        $\BIR(t) = \tildeO\rbr{t^{-\gamma}}$
    for all $t$ and some $\gamma>0$, then $\gamma \leq \nicefrac{1}{2}$.

>>>>

\item Exploration-separating algorithms can achieve
    $\BIR(t) = \tildeO\rbr{t^{-1/3}}$
for all priors, \eg by using Epsilon-Greedy algorithm with exploration probability $\eps_t = t^{-1/3}$ in each round $t$.
In the typical scenario when
 $\BReg(t)\geq \Omega(t^{2/3})$,
the \BIR rate of $t^{-1/3}$  cannot be improved, in the following sense:
if
    $\BIR(t) = \tildeO\rbr{t^{-\gamma}}$
for all $t$, then $\gamma\geq \nicefrac{1}{3}$.

\item Adaptive-exploration algorithms \emph{can} have an even better regret rate: $\BIR(t) = \tildeO\rbr{ t^{-1/2} } $. This holds for Successive Elimination \citep{EvenDar-icml06} and for Thompson Sampling (see Appendix~\ref{app:examples}).% 
    \footnote{However, such result is not known for UCB1 algorithm, to the best of our knowledge.}
    Any optimal MAB algorithm enjoys this regret rate ``on average" by \eqref{eq:bg-BReg}, since 
        $\BReg(T)\leq \tildeO(\sqrt{T})$.
    In particular, if such algorithm satisfies
        $\BIR(t) = \tildeO\rbr{t^{-\gamma}}$
    for all $t$, then $\gamma \leq \nicefrac{1}{2}$.
